Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-18 chi2012.tex
a  few more

The second finding is that equivalent properties were sometimes, though only rarely, given the same name.  Thus, terminological heterogeneity was prevalent across data records we observed.  Structural heterogeneity, however, was comparatively rare, with the most common case being similar to the birthday example above; a leaf property on one record modeled as a subtree in the other.  We also encountered, particularly in the Weather category, examples of fields which had data embedded in textual description fields

>>>>

The second finding is that equivalent properties were sometimes, though only rarely, given the same name.  Thus, terminological heterogeneity was prevalent across data records we observed.  Structural heterogeneity, however, was comparatively rare, with the most common case being similar to the birthday example above; a leaf property on one record modeled as a subtree in the other.  We also encountered, particularly in the Weather category, examples of fields which had data embedded in textual description fields, which hints their intended use in RSS and other feed readers than as stuctured data feeds.

Modelling
